### 2013-01-19 draft.tex
save

\newpage
\section*{Introduction}
\addcontentsline{toc}{section}{Introduction}
1-2 pages
adssdadas

>>>>

\newpage
\section*{Introduction}
\addcontentsline{toc}{section}{Introduction}
In our generation scientific and engineering community attempts to build a human-like machine.
Like a man, these robots are supposed to have various senses, ability to analyse incoming information, based on its done conclusions and develop and implement behaviour patterns.
And starting to realize, scientists immediately came across a problem of image understanding.
There are a lot of engineering achievements that supersede analogues in the most perfect system - human.
However, there is a large gap in the technology of artificial intelligence.
Impossibility to fully automatic analysis of information from visual channel, even as a child does, pushes researchers to move forward gradually.
They divide the problem into sub-problems of computer vision. 
For example, improve image quality, identify features points and determine the similarity of images.

The vision channel is one of the most informative one.
Data volume from video stream exceeds by several times volumes from other sensors.
Here lies the pitfall - redundancy of information.
%Иногда бывает достаточно нескольких байт информации
Occasionally it's just a few bytes of information.
For example, we need only the object of interest, and in addition to this, we have other objects, background and fine details.
